---
title: "Questionnaire Analysis"
output: html_notebook
---


```{r}
library(ggplot2)
library(tidyverse)
```

```{r}
df <- read.csv("Social Environment.csv")

colnames(df)[4] <- 'I_E'
colnames(df)[5] <- 'dg_go_noone'
colnames(df)[6] <- 'dg_soc_noone'
colnames(df)[7] <- 'fb_go_noone'
colnames(df)[8] <- 'fb_soc_noone'
colnames(df)[9] <- 'fb_go_alot'
colnames(df)[10] <- 'fb_soc_alot'
colnames(df)[11] <- 'ask_to_hang_out'

colnames(df)[12] <- 'SE_place_for_meeting_and_connections'
colnames(df)[13] <- 'SE_place_for_deeper_connections'
colnames(df)[14] <- 'FB_place_for_meeting_and_connections'
colnames(df)[15] <- 'FB_place_for_deeper_connections'
colnames(df)[16] <- 'hard_to_contact_new_people'
colnames(df)[17] <- 'natural_to_take_initiative'
colnames(df)[18] <- 'easier_same_sex_connection'
colnames(df)[19] <- 'easier_similar_I_E'
colnames(df)[20] <- 'easier_socialise_not_taking_initiative'
colnames(df)[21] <- 'more_likely_to_go_if_knowing_more_people'
colnames(df)[22] <- 'would_like_to_socialise_more'
colnames(df)[23] <- 'would_like_a_larger_network'
colnames(df)[24] <- 'would_like_more_close_friends'
colnames(df)[25] <- 'social_contributes'
colnames(df)[26] <- 'cog_sci_social_environment_is_special'


df


```
```{r}
#friday bar deep connections
df <-
  mutate(transform(df, FB_place_for_deeper_connections = as.integer(as.character(
       factor(FB_place_for_deeper_connections, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#small event deep connections
df <-
  mutate(transform(df, SE_place_for_deeper_connections = as.integer(as.character(
       factor(SE_place_for_deeper_connections, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#SE_place_for_meeting_and_connections
df <-
  mutate(transform(df, SE_place_for_meeting_and_connections = as.integer(as.character(
       factor(SE_place_for_meeting_and_connections, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#FB_place_for_meeting_and_connections
df <-
  mutate(transform(df, FB_place_for_meeting_and_connections = as.integer(as.character(
       factor(FB_place_for_meeting_and_connections, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#hard_to_contact_new_people
df <-
  mutate(transform(df, hard_to_contact_new_people = as.integer(as.character(
       factor(hard_to_contact_new_people, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))
#easier for same sex
df <-
  mutate(transform(df, easier_same_sex_connection = as.integer(as.character(
       factor(easier_same_sex_connection, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))


#easier_similar_I_E
df <-
  mutate(transform(df, easier_similar_I_E = as.integer(as.character(
       factor(easier_similar_I_E, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#natural_to_take_initiative
df <-
  mutate(transform(df, natural_to_take_initiative = as.integer(as.character(
       factor(natural_to_take_initiative, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#easier_socialise_not_taking_initiative
df <-
  mutate(transform(df, easier_socialise_not_taking_initiative = as.integer(as.character(
       factor(easier_socialise_not_taking_initiative, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#more_likely_to_go_if_knowing_more_people
df <-
  mutate(transform(df, more_likely_to_go_if_knowing_more_people = as.integer(as.character(
       factor(more_likely_to_go_if_knowing_more_people, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#would_like_to_socialise_more
df <-
  mutate(transform(df, would_like_to_socialise_more = as.integer(as.character(
       factor(would_like_to_socialise_more, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#would_like_a_larger_network
df <-
  mutate(transform(df, would_like_a_larger_network = as.integer(as.character(
       factor(would_like_a_larger_network, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#would_like_more_close_friends
df <-
  mutate(transform(df, would_like_more_close_friends = as.integer(as.character(
       factor(would_like_more_close_friends, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#social_contributes
df <-
  mutate(transform(df, social_contributes = as.integer(as.character(
       factor(social_contributes, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))

#cog_sci_social_environment_is_special
df <-
  mutate(transform(df, cog_sci_social_environment_is_special = as.integer(as.character(
       factor(cog_sci_social_environment_is_special, 
         levels = c("Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree"),
         labels = c(1, 2, 3, 4, 5, 6, 7)
       )
 ))))
```

```{r}

df

df$I_E <- as.integer(df$I_E)

df %>%
ggplot(aes(x = I_E, fill = I_E)) +
  geom_bar()


df$easier_similar_I_E <- as.factor(df$easier_similar_I_E)
unique(df$easier_similar_I_E)

df %>%
  mutate(easier_similar_I_E = fct_relevel(easier_similar_I_E, 
            "Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree")) %>%
  ggplot(aes(x = easier_similar_I_E, fill = easier_similar_I_E)) +
  geom_bar() +
  facet_wrap(~I_E) +
  labs(title = "easier_similar_I_E") +
  theme(axis.text.x=element_blank(), axis.ticks=element_blank())

```

```{r}

df

df$would_like_a_larger_network <- as.factor(df$would_like_a_larger_network)
unique(df$would_like_a_larger_network)

df %>%
  mutate(would_like_a_larger_network = fct_relevel(would_like_a_larger_network, 
            "Strongly Disagree", "Disagree", "Somewhat disagree", "Neutral", "Somewhat agree", "Agree",
            "Strongly agree")) %>%
  ggplot(aes(x = would_like_a_larger_network, fill = would_like_a_larger_network)) +
  geom_bar() +
  facet_wrap(~I_E) +
  labs(title = "would_like_a_larger_network") +
  theme(axis.text.x=element_blank(), axis.ticks=element_blank())

```
#dont know if this is any good use really

```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(dg_go_noone), sd(dg_go_noone))
```
#as expected, the more extraverted you are, the more likely you are to go if you know no one at a dinner group
```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(fb_go_noone), sd(fb_go_noone))

df %>%
  summarise(mean(fb_go_noone), sd(fb_go_noone))
```
#it kind of wavers on how likely, the least likely is I_E, 3 followed by 1 and 5, overall more reversed about going to a friday bar alone than a dinner group
```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(fb_go_alot), sd(fb_go_alot))
```
#overall increase if they know more people, therefore i think this is something we should use as it justifies why more people should go to the event if they know more people
```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(fb_soc_noone), sd(fb_soc_noone))
```
#comfort on socialising when they know no one increases with IE with that random 5 in there
```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(fb_soc_alot), sd(fb_soc_alot))
```
#once again, i think friends is a justifiable measure here, as for the lower level introverts it makes a big difference

```{r}
plotty <- df %>%
  group_by(I_E) %>%
  summarise(mean(easier_socialise_not_taking_initiative), sd(easier_socialise_not_taking_initiative))

plotty <- plotty %>% 
  rename(
    easier = 'mean(easier_socialise_not_taking_initiative)',
    )


plotty <- plotty %>% 
  rename(
    sd = 'sd(easier_socialise_not_taking_initiative)',
    )


plotty$I_E <- as.factor(plotty$I_E)

ggplot(plotty, aes(fill= I_E, y= easier, x= I_E)) +
  geom_bar(position='dodge', stat='identity') +
  labs(title = "Easier to Socialise Not Taking Initiative Depending on I-E Score", x= "I_E", y = "Mean of Agreement", subtitle = "Agreement Scale: 1 = Strongly Disagree, 7 = Strongly Agree") +
  geom_errorbar(aes(ymin=easier-sd, ymax=easier+sd, width=.2))
  

```
#people asked to hangout is increased the more ex u come, we can use this

```{r}
df %>%
  summarise(mean(social_contributes), sd(social_contributes))
```
# social events contribute, leaning towards somewhat agree more than neutral
```{r}
df %>%
  summarise(mean(cog_sci_social_environment_is_special), sd(cog_sci_social_environment_is_special))
```
# Sitting comfortably at agree
```{r}
df %>%
  group_by(I_E) %>%
  summarise(mean(SE_place_for_deeper_connections), sd(SE_place_for_deeper_connections))

df %>%
  summarise(mean(FB_place_for_deeper_connections), sd(FB_place_for_deeper_connections))
```
# neutral, so sex doesnt make a difference on connection

```{r}
df %>%
  summarise(mean(cog_sci_social_environment_is_special), sd(cog_sci_social_environment_is_special))
```

```{r}
df %>%
  summarise(mean(easier_), sd(easier_same_sex_connection))
```






