---
title: "Network Analysis for Validation"
author: "Emma Rose and Mie"
date: "05/06/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("~/SocCult/abm_soccult")
```

## Table of content

Template of Network Analysis used from Riccardo template given in class. We are using this to load in and visualize the 2019 first semester data, and then to use quantification to validate our ABM network agaisnt the 2019 dataset. 


There's 3 parts:
1. Visualization
2. Quantification 
3. Community detection

First we load the data for 2019

```{r Load data}
pacman::p_load(tidyverse,
               here,
               network,
               igraph,
               ggraph,
               tidygraph,
               patchwork)

CogSci_2019_n1_edges <- read_csv(
  here("CogSci19S1_NetworkFriends.csv")) %>% 
  subset(
    !is.na(to) & !is.na(from) & !is.na(weight))

# Creating a list of unique IDs across the 3 datasets
CogSci_2019_nodes <- data.frame(ID=unique(c(
  CogSci_2019_n1_edges$from,
  CogSci_2019_n1_edges$to)))

citation('igraph')
```

Then we visualize the data

```{r}

# Remove data from people being funny

CogSci_2019_nodes <- CogSci_2019_nodes %>% subset(
   !(ID %in% c("fake0", "fake", "100", "1")) & !is.na(ID)
)
 

CogSci_2019_n1_edges <- CogSci_2019_n1_edges %>% subset(
  !(to %in% c("fake0", "fake", "100", "1")) & !(from %in% c("fake0", "fake", "100", "1") & !is.na(to) & !is.na(from))
)

```

```{r}
# Create the graph from semester 1
CogSci_2019_n1_igraph <-
  graph_from_data_frame(d = CogSci_2019_n1_edges,
                        vertices = CogSci_2019_nodes,
                        directed = TRUE)

CogSci_2019_n1_igraph <-
  graph_from_data_frame(d = CogSci_2019_n1_edges,
                        vertices = CogSci_2019_nodes,
                        directed = TRUE)

E(CogSci_2019_n1_igraph)$arrow.mode <- 0
V(CogSci_2019_n1_igraph)$label <- ""
V(CogSci_2019_n1_igraph)$frame.color <- "white"
V(CogSci_2019_n1_igraph)$color <- "pink"
E(CogSci_2019_n1_igraph)$width <- edge_attr(CogSci_2019_n1_igraph)$weight

deg1 <- degree(CogSci_2019_n1_igraph, mode="all")
V(CogSci_2019_n1_igraph)$size <- deg1

p1<-plot(CogSci_2019_n1_igraph,
     layout = layout_on_sphere, # Explore layouts!
     edge.arrow.size = 0.2)
```

```{r}
plot(CogSci_2019_n1_igraph,
     layout = layout_nicely, # Explore layouts!
     edge.arrow.size = 0.2)
```

#All together

Quantification

```{r}
summary(degree(CogSci_2019_n1_igraph))

```


```{r}
#degree_distribution(network_cleaned)


par(mfrow=c(1,2))

mean(degree(network_cleaned))
mean(degree(CogSci_2019_n1_igraph))
sd(degree(CogSci_2019_n1_igraph))

ABM_D <- degree(network_cleaned)
CogSci_Real_D <- degree(CogSci_2019_n1_igraph) 

t.test(ABM_D, CogSci_Real_D)

mean(degree_distribution(network_cleaned))
mean(degree_distribution(CogSci_2019_n1_igraph))

DegreeDistr_ABM <- degree_distribution(network_cleaned)
DegreeDistr_2019 <- degree_distribution(CogSci_2019_n1_igraph)

#t.test(DegreeDistr_ABM, DegreeDistr_2019)

# Degree

rethinking::dens(degree_distribution(network_cleaned))+
  title("ABM Degree Distribution")
rethinking::dens(degree_distribution(CogSci_2019_n1_igraph))+
  title("2019 Data Degree Distribution")



# Average path length

mean_distance(network_cleaned, directed = TRUE, unconnected = TRUE)
mean_distance(CogSci_2019_n1_igraph, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned)
transitivity(CogSci_2019_n1_igraph)

Transitivity_ABM <- transitivity(network_cleaned, type = 'local')
Transitivity_2019 <-transitivity(CogSci_2019_n1_igraph, type = 'local')

t.test(Transitivity_ABM, Transitivity_2019) 
## Centrality

mean(betweenness(network_cleaned))
rethinking::dens(betweenness(network_cleaned))+
  title("ABM Betweenness Centrality")
mean(betweenness(CogSci_2019_n1_igraph))
rethinking::dens(betweenness(CogSci_2019_n1_igraph))+
  title("2019 Data Betweenness Centrality")

Betweenness_ABM <- betweenness(network_cleaned)
Betweenness_2019 <- betweenness(CogSci_2019_n1_igraph)

t.test(Betweenness_ABM, Betweenness_2019) 


mean(eigen_centrality(network_cleaned)$vector)
mean(eigen_centrality(CogSci_2019_n1_igraph)$vector)

Eigen_ABM <- eigen_centrality(network_cleaned)$vector
Eigen_2019 <- eigen_centrality(CogSci_2019_n1_igraph)$vector

t.test(Eigen_ABM, Eigen_2019)


```


## 60 Days : Joint and Big

```{r}
#Comparing only small and big events for 60 days

network_cleaned_joint60 <- network_cleaned_joint_60
network_cleaned_big60 <- network_cleaned_big_60

par(mfrow=c(1,2))

mean(degree(network_cleaned_joint60))
mean(degree(network_cleaned_big60))

J60_D <- degree(network_cleaned_joint60)
BE60_D <- degree(network_cleaned_big60) 

t.test(BE60_D, J60_D)

mean(degree_distribution(network_cleaned_joint60))
mean(degree_distribution(network_cleaned_big60))

DegreeDistr_J60 <- degree_distribution(network_cleaned_joint60)
DegreeDistr_BE60 <- degree_distribution(network_cleaned_big60)

t.test(DegreeDistr_ABM, DegreeDistr_2019)

# Degree

rethinking::dens(degree_distribution(network_cleaned_joint60))+
  title("Small Event Degree Distribution 60")
rethinking::dens(degree_distribution(network_cleaned_big60))+
  title("Big Event Degree Distribution 60")



# Average path length

mean_distance(network_cleaned_joint60, directed = TRUE, unconnected = TRUE)
mean_distance(network_cleaned_big60, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned_joint60)
transitivity(network_cleaned_big60)

Transitivity_J60 <- transitivity(network_cleaned_joint60, type = 'local')
Transitivity_BE60 <-transitivity(network_cleaned_big60, type = 'local')

t.test(Transitivity_BE60, Transitivity_J60) 
## Centrality

mean(betweenness(network_cleaned_joint60))
rethinking::dens(betweenness(network_cleaned_joint60))+
  title("Small Event 60 Betweenness Centrality")
mean(betweenness(network_cleaned_big60))
rethinking::dens(betweenness(network_cleaned_big60))+
  title("Big Event 60 Betweenness Centrality")

Betweenness_J60 <- betweenness(network_cleaned_joint60)
Betweenness_BE60 <- betweenness(network_cleaned_big60)

t.test(Betweenness_BE60, Betweenness_J60) 


mean(eigen_centrality(network_cleaned_joint60)$vector)
mean(eigen_centrality(network_cleaned_big60)$vector)

Eigen_J60 <- eigen_centrality(network_cleaned_joint60)$vector
Eigen_BE60 <- eigen_centrality(network_cleaned_big60)$vector

t.test(Eigen_BE60, Eigen_J60)


```

#60 days : Small and Big
```{r}
#Comparing only small and big events for 60 days

network_cleaned_small60 <- network_cleaned_small_60
network_cleaned_big60 <- network_cleaned_big_60

par(mfrow=c(1,2))

mean(degree(network_cleaned_small60))
mean(degree(network_cleaned_big60))

SE60_D <- degree(network_cleaned_small60)
BE60_D <- degree(network_cleaned_big60) 

t.test(BE60_D, SE60_D)

mean(degree_distribution(network_cleaned_small60))
mean(degree_distribution(network_cleaned_big60))

DegreeDistr_SE60 <- degree_distribution(network_cleaned_small60)
DegreeDistr_BE60 <- degree_distribution(network_cleaned_big60)

#t.test(DegreeDistr_ABM, DegreeDistr_2019)

# Degree

rethinking::dens(degree_distribution(network_cleaned_small60))+
  title("Small Event Degree Distribution 60")
rethinking::dens(degree_distribution(network_cleaned_big60))+
  title("Big Event Degree Distribution 60")



# Average path length

mean_distance(network_cleaned_small60, directed = TRUE, unconnected = TRUE)
mean_distance(network_cleaned_big60, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned_small60)
transitivity(network_cleaned_big60)

Transitivity_SE60 <- transitivity(network_cleaned_small60, type = 'local')
Transitivity_BE60 <-transitivity(network_cleaned_big60, type = 'local')

t.test(Transitivity_BE60, Transitivity_SE60) 
## Centrality

mean(betweenness(network_cleaned_small60))
rethinking::dens(betweenness(network_cleaned_small60))+
  title("Small Event 60 Betweenness Centrality")
mean(betweenness(network_cleaned_big60))
rethinking::dens(betweenness(network_cleaned_big60))+
  title("Big Event 60 Betweenness Centrality")

Betweenness_SE60 <- betweenness(network_cleaned_small60)
Betweenness_BE60 <- betweenness(network_cleaned_big60)

t.test(Betweenness_BE60, Betweenness_SE60) 


mean(eigen_centrality(network_cleaned_small60)$vector)
mean(eigen_centrality(network_cleaned_big60)$vector)

Eigen_SE60 <- eigen_centrality(network_cleaned_small60)$vector
Eigen_BE60 <- eigen_centrality(network_cleaned_big60)$vector

t.test(Eigen_BE60, Eigen_SE60)


```



## 120 Days : Joint and Big

```{r}
#Comparing only small and big events for 60 days

network_cleaned_joint120 <- network_cleaned_joint_120
network_cleaned_big120 <- network_cleaned_big_120

par(mfrow=c(1,2))

mean(degree(network_cleaned_joint120))
mean(degree(network_cleaned_big120))

J120_D <- degree(network_cleaned_joint120)
BE120_D <- degree(network_cleaned_big120) 

t.test(BE120_D, J120_D)

mean(degree_distribution(network_cleaned_joint120))
mean(degree_distribution(network_cleaned_big120))

DegreeDistr_J60 <- degree_distribution(network_cleaned_joint120)
DegreeDistr_BE60 <- degree_distribution(network_cleaned_big120)

t.test(DegreeDistr_BE60, DegreeDistr_J60)

# Degree

rethinking::dens(degree_distribution(network_cleaned_joint120))+
  title("Small Event Degree Distribution 120")
rethinking::dens(degree_distribution(network_cleaned_big120))+
  title("Big Event Degree Distribution 120")



# Average path length

mean_distance(network_cleaned_joint120, directed = TRUE, unconnected = TRUE)
mean_distance(network_cleaned_big120, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned_joint120)
transitivity(network_cleaned_big120)

Transitivity_J120 <- transitivity(network_cleaned_joint120, type = 'local')
Transitivity_BE120 <-transitivity(network_cleaned_big120, type = 'local')

t.test(Transitivity_BE120, Transitivity_J120) 
## Centrality

mean(betweenness(network_cleaned_joint120))
rethinking::dens(betweenness(network_cleaned_joint120))+
  title("Small Event 120 Betweenness Centrality")
mean(betweenness(network_cleaned_big120))
rethinking::dens(betweenness(network_cleaned_big120))+
  title("Big Event 120 Betweenness Centrality")

Betweenness_J120 <- betweenness(network_cleaned_joint120)
Betweenness_BE120 <- betweenness(network_cleaned_big120)

t.test(Betweenness_BE120, Betweenness_J120) 


mean(eigen_centrality(network_cleaned_joint120)$vector)
mean(eigen_centrality(network_cleaned_big120)$vector)

Eigen_J120 <- eigen_centrality(network_cleaned_joint120)$vector
Eigen_BE120 <- eigen_centrality(network_cleaned_big120)$vector

t.test(Eigen_BE120, Eigen_J120)


```
#120 days

```{r}
citation()
```

```{r}
#Comparing only small and big events for 120 days

network_cleaned_small120 <- network_cleaned_small_120
network_cleaned_big120 <- network_cleaned_big_120

par(mfrow=c(1,2))

mean(degree(network_cleaned_small120))
mean(degree(network_cleaned_big120))

SE120_D <- degree(network_cleaned_small120)
BE120_D <- degree(network_cleaned_big120) 

t.test(BE120_D, SE120_D)

mean(degree_distribution(network_cleaned_small120))
mean(degree_distribution(network_cleaned_big120))

DegreeDistr_SE120 <- degree_distribution(network_cleaned_small120)
DegreeDistr_BE120 <- degree_distribution(network_cleaned_big120)

t.test(DegreeDistr_BE120, DegreeDistr_SE120)

# Degree

rethinking::dens(degree_distribution(network_cleaned_small120))+
  title("Small Event Degree Distribution 120")
rethinking::dens(degree_distribution(network_cleaned_big120))+
  title("Big Event Degree Distribution 120")



# Average path length

mean_distance(network_cleaned_small120, directed = TRUE, unconnected = TRUE)
mean_distance(network_cleaned_big120, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned_small120)
transitivity(network_cleaned_big120)

Transitivity_SE120 <- transitivity(network_cleaned_small120, type = 'local')
Transitivity_BE120 <-transitivity(network_cleaned_big120, type = 'local')

t.test(Transitivity_BE120, Transitivity_SE120) 
## Centrality

mean(betweenness(network_cleaned_small120))
rethinking::dens(betweenness(network_cleaned_small120))+
  title("Small Event 120 Betweenness Centrality")
mean(betweenness(network_cleaned_big120))
rethinking::dens(betweenness(network_cleaned_big120))+
  title("Big Event 120 Betweenness Centrality")

Betweenness_SE120 <- betweenness(network_cleaned_small120)
Betweenness_BE120 <- betweenness(network_cleaned_big120)

t.test(Betweenness_BE120, Betweenness_SE120) 


mean(eigen_centrality(network_cleaned_small120)$vector)
mean(eigen_centrality(network_cleaned_big120)$vector)

Eigen_SE120 <- eigen_centrality(network_cleaned_small120)$vector
Eigen_BE120 <- eigen_centrality(network_cleaned_big120)$vector

t.test(Eigen_BE120, Eigen_SE120)
```


# 4 Community Detection

```{r}
#making the networks look the same for easier comparing
E(network_cleaned)$arrow.mode <- 0
V(network_cleaned)$label <- ""

# Community detection
wc1 <- cluster_walktrap(network_cleaned)
# wc1 <- cluster_infomap(as.undirected(network_cleaned))
modularity(wc1)
membership(wc1)

wc2 <- cluster_walktrap(CogSci_2019_n1_igraph)
modularity(wc2)
membership(wc2)


par(mfrow=c(1,2))

plot(wc1, network_cleaned, layout = layout_nicely)
plot(wc2, CogSci_2019_n1_igraph)


# Community detection (by optimizing modularity over partitions):
clp <- cluster_louvain(as.undirected(network_cleaned))
plot(clp, network_cleaned, layout = layout_nicely, edge.arrow.size = 0.2)


clp <- cluster_louvain(as.undirected(CogSci_2019_n1_igraph))
plot(clp, CogSci_2019_n1_igraph, layout = layout_nicely, edge.arrow.size = 0.2)


#clop <- cluster_optimal(CogSci_2019_n1_igraph)
#plot(clop, CogSci_2019_n1_igraph)

#par(mfrow=c(1,1))
```

