---
title: "Network Analysis for Validation of 60 Ticks"
author: "Emma Rose Hahn and Mie Buchhave Søgaard"
date: "09/06/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/SocCult/abm_soccult")
```

## Table of content

Template of Network Analysis used from Riccardo template given in class. We are using this to load in and visualize the 2019 first semester data, and then to use quantification to validate our ABM network agaisnt the 2019 dataset. 


There's 3 parts:
1. Visualization
2. Quantification 
3. Community detection

First we load the data for 2019

```{r Load data}
pacman::p_load(tidyverse,
               here,
               network,
               igraph,
               ggraph,
               tidygraph,
               patchwork)

CogSci_2019_n1_edges <- read_csv(
  here("CogSci19S1_NetworkFriends.csv")) %>% 
  subset(
    !is.na(to) & !is.na(from) & !is.na(weight))

# Creating a list of unique IDs across the 3 datasets
CogSci_2019_nodes <- data.frame(ID=unique(c(
  CogSci_2019_n1_edges$from,
  CogSci_2019_n1_edges$to)))

```

Then we visualize the data

```{r}

# Remove data from people being funny

CogSci_2019_nodes <- CogSci_2019_nodes %>% subset(
   !(ID %in% c("fake0", "fake", "100", "1")) & !is.na(ID)
)
 

CogSci_2019_n1_edges <- CogSci_2019_n1_edges %>% subset(
  !(to %in% c("fake0", "fake", "100", "1")) & !(from %in% c("fake0", "fake", "100", "1") & !is.na(to) & !is.na(from))
)

```

```{r}
# Create the graph from semester 1
CogSci_2019_n1_igraph <-
  graph_from_data_frame(d = CogSci_2019_n1_edges,
                        vertices = CogSci_2019_nodes,
                        directed = TRUE)

CogSci_2019_n1_igraph <-
  graph_from_data_frame(d = CogSci_2019_n1_edges,
                        vertices = CogSci_2019_nodes,
                        directed = TRUE)

E(CogSci_2019_n1_igraph)$arrow.mode <- 0
V(CogSci_2019_n1_igraph)$label <- ""
V(CogSci_2019_n1_igraph)$frame.color <- "white"
V(CogSci_2019_n1_igraph)$color <- "pink"
E(CogSci_2019_n1_igraph)$width <- edge_attr(CogSci_2019_n1_igraph)$weight

deg1 <- degree(CogSci_2019_n1_igraph, mode="all")
V(CogSci_2019_n1_igraph)$size <- deg1

p1<-plot(CogSci_2019_n1_igraph,
     layout = layout_on_sphere, # Explore layouts!
     edge.arrow.size = 0.2)
```

```{r}
plot(CogSci_2019_n1_igraph,
     layout = layout_nicely, # Explore layouts!
     edge.arrow.size = 0.2)
```

#All together

Quantification


```{r}
#degree_distribution(network_cleaned)


par(mfrow=c(1,2))

mean(degree(network_cleaned))
mean(degree(CogSci_2019_n1_igraph))

ABM_D <- degree(network_cleaned)
CogSci_Real_D <- degree(CogSci_2019_n1_igraph) 

t.test(ABM_D, CogSci_Real_D)

mean(degree_distribution(network_cleaned))
mean(degree_distribution(CogSci_2019_n1_igraph))

DegreeDistr_ABM <- degree_distribution(network_cleaned)
DegreeDistr_2019 <- degree_distribution(CogSci_2019_n1_igraph)

#t.test(DegreeDistr_ABM, DegreeDistr_2019)

# Degree

rethinking::dens(degree_distribution(network_cleaned))+
  title("ABM Degree Distribution")
rethinking::dens(degree_distribution(CogSci_2019_n1_igraph))+
  title("2019 Data Degree Distribution")



# Average path length

mean_distance(network_cleaned, directed = TRUE, unconnected = TRUE)
mean_distance(CogSci_2019_n1_igraph, directed = TRUE, unconnected = TRUE)

# Clustering coefficient

transitivity(network_cleaned)
transitivity(CogSci_2019_n1_igraph)

Transitivity_ABM <- transitivity(network_cleaned, type = 'local')
Transitivity_2019 <-transitivity(CogSci_2019_n1_igraph, type = 'local')

t.test(Transitivity_ABM, Transitivity_2019) 
## Centrality

mean(betweenness(network_cleaned))
rethinking::dens(betweenness(network_cleaned))+
  title("ABM Betweenness Centrality")
mean(betweenness(CogSci_2019_n1_igraph))
rethinking::dens(betweenness(CogSci_2019_n1_igraph))+
  title("2019 Data Betweenness Centrality")

Betweenness_ABM <- betweenness(network_cleaned)
Betweenness_2019 <- betweenness(CogSci_2019_n1_igraph)

t.test(Betweenness_ABM, Betweenness_2019) 


mean(eigen_centrality(network_cleaned)$vector)
mean(eigen_centrality(CogSci_2019_n1_igraph)$vector)

Eigen_ABM <- eigen_centrality(network_cleaned)$vector
Eigen_2019 <- eigen_centrality(CogSci_2019_n1_igraph)$vector

t.test(Eigen_ABM, E_2019)


```
